Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
Moar intro

>>>>

One method of exploring, and then compressing, the hierarchical structure of
data is to transform the data into a grammar.  The \Sequitur algorithm of
\cite{sequitur} does exactly this, demonstrating how context-free grammars in
particular offer a means of simultaneously revealing the structure of data
inputs and compressing it efficiently.  However, inspection of \Sequitur's
results reveals that it is unable to detect and to compress larger scale
structure because of the aforementioned low-level fluctuations.

We are interested in whether lossy compression techniques can be combined with
CFG transformation and compression techniques like \Sequitur's in order (a) to
illuminate the high-level grammatical structure of the data, and (b) to more
effectively compress the data with some tolerable degree of lossiness.  That
is, our goals are twofold---we wish to develop a technique which can both
increase human understanding of a complex document and yield good compression
ratios.  Notably, if we are interested in the structure rather than the
details, we surmise that the lossiness we introduce can be highly desirable.
For instance, introducing lossiness to \Sequitur's transformation on musical
passages could result in interesting, even music-theoretically sound
reductions, of a given piece.
